---
title: "今年迄5/25上午5am各鄉鎮市區"
subtitle: "每十萬人口的新冠病毒本土個案"
output:
  prettydoc::html_pretty:
    theme: hpstr
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Cases per 100,000 people by district for locally acquired covid cases in Taiwan
## time period:01/01/2021 to 05/25/2021 @ 5am

```{r incidence map script, include=FALSE}
#gets us in the right working directory
setwd("C:/Users/rshea/Desktop/old computer/Covid")

#stuff to do in console
# library(rmarkdown)
#render("525covidmap.Rmd")

#this runs the incidence map scripts
source("Incidence_map_script.R")

```


```{r Prevalence map, echo=FALSE}
require(tmap)
tmap_mode("view")
cases_per_hundred_thousand.map
```

For more Taiwanese covid maps and commentary about Taiwan's current outbreak: https://tulipsfortaiwan.blogspot.com/p/maps-of-taiwans-covid-outbreak.html 

### Notes
1. This map shows the number of cases per 100,000 people for each district from  01/01/2021 to 05/25/2021 at 5AM
本地圖顯示今年初迄05/25/2021上午5點
的各鄉鎮市區每十萬人口的本土個案
   
   本土個案數據來源 Data source for case numbers:     https://nidss.cdc.gov.tw/nndss/DiseaseMap?id=19CoV

2. Population data is from 2017. 人口為106年的人口
   
   Population data source人口數據來源： https://data.gov.tw/dataset/8410

3. The Code used to make this map is available at: 
https://github.com/TulipsforTaiwan/TaiwanCovid

4. Color scale is non-continuous, Wanhua has 4-5 times more cases per 100,000 people than any other township in Taiwan

-----